Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-02-09 article.tex
typos

@@

%binvincular 
\newcommand{\x}{X}
\newcommand{\y}{Y}
\newcommand{\bmotif}{(\sigma,\x,\y)}

\newcommand{\pbmotif}{\pmotif^+}
\newcommand{\pbmotifX}{\x_{\pbmotif}}
\newcommand{\pbmotifY}{\y_{\pbmotif}}

%LSC
\DeclareMathOperator{\LCSa}{LCS}
\newcommand{\LCS}[8]{\LCSa_{{#1},{#2},{#3}}^{{#4},{#5},{#6}}({#7},{#8})}

\DeclareMathOperator{\matcha}{MATCH}
\newcommand{\match}[8]{\matcha_{{#1},{#2},{#3}}^{{#4},{#5},{#6}}({#7},{#8})}

@@

A \emph{bivincular pattern} (abbreviated BVP) $\sigma$
of length $k$ is a permutation in $S_k$ written in
two-line notation 
(that is the top row is $12\,\ldots\,k$ and the bottom row
is a permutation $\sigma_1\sigma_2\,\ldots\,\sigma_k$).
We have the following conditions on the top and bottom rows
of $\sigma$:
\begin{itemize}
	\item
	If the bottom line of $\sigma$ contains
	$\underline{\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j}$
	then the letters corresponding to 
	$\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j$ in an occurrence of
	$\sigma$ in a permutaton must be adjacent, whereas there is
	no adjacency condition for
	non-underlined consecutive letters.
	Moreover if the bottom row of $\sigma$ begins with
	$_\llcorner{\sigma_1}$ then any occurrence of $\sigma$ 
	in a permutation $\pi$ must begin with the leftmost 
	letter of $\pi$,
	and 
	if the bottom row of $\sigma$ begins with
	${\sigma_k}_\lrcorner$ then any occurrence of $\sigma$ 
	in a permutation $\pi$ must end with the rightmost 
	letter of $\pi$.
	\item
	If the top line of $\sigma$ contains
	$\overline{i\,i+1\,\ldots\,j}$ then the letters corresponding to
	$\sigma_i, \sigma_{i+1}, \ldots, \sigma_j$ in an
	occurrence of $\sigma$ in a permutation must be adjacent in values,
	whereas there is no value adjacency restriction for non-overlined 
	letters.
	Moreover, if the top row of $\sigma$ begins with
	$^\ulcorner{1}$ then
	any occurrence of $\sigma$ is a permutation $\pi$ must begin with
	the smallest letter of $\pi$, and
	if top row of $\sigma$ ends with $k^\urcorner$ then
	any occurrence of $\sigma$ is a permutation $\pi$ must end with
	the largest letter of $\pi$.
\end{itemize}
Given a motif $\pmotif$ we represent the elements underlined by the set $\x$. An index $i$ of an element is in $\x$ if and only if $i$ and $i+1$ need to be adjacent ($\pmotif[i]$ and $\pmotif[i+1]$ are underlined).
For example if we have $\underline{\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j}$, then ${i,i+1,\ldots,j-1} \in \y$. 
We represent the index that need to be overlined by the set $\y$. An index $i$ is in $\y$ if and only if $i$ and $i+1$ need to be adjacent ($i$ and $i+1$ are overlined).
For example if we have
For example if we have $\overline{i\,i+1\,\ldots\,j}$, then ${i,i+1,\ldots,j-1} \in \y$.
% A bivincular pattern avoids a set of permutations $P$ if its bottom
% row $\sigma_1\sigma_2\,\ldots\,\sigma$ avoids every permutation in $P$.

@@

This section focus on the pattern matching problem when only the motif avoid $(213,231)$.

\begin{proposition}
Let $\pmotif$, $\ptext$ 
be two permutation,
with  $\pmotif$ a permutation avoiding (231,213), 
we can decide in $O(|\pmotif||\ptext|^2)$ time
and $O(|\pmotif||\ptext|^2)$ space
if $\pmotif$ 
is a motif of $\ptext$.
\end{proposition}

%			\textbf{Proof}
%			The main point is that
%			if we match a ascnt (descent) element $i_{\pmotif}$ of the motif
%			with an element $i_{\ptext}$ of the text,
%			the optimal way of matching
%			the first previous ascnt (descent)
%			that appear before an descent (ascent)
%			is to choose the
%			maximal (minimal) element possible.
%			Indeed if we do not take
%			the maximal (minimal) element,
%			we may prevent some element
%			in the future matching.\\

For the proof and the algorithm we introduce a decomposition : we decompose the stripe of the motif into factor of same letter, and label those factor from right to left. We also need to add the last index into the first factor. For each factor, we denote the left most element by $\firsta$. For example, given the motif $981237654$, $\factor{1} =7654$, $\first{1}=7$, $\factor{2}=123$, $\first{2}=1$, $\factor{3}=98$ and $\first{9}$. \\

\begin{proof}
Given an ascent (descent) factor $\factor{i}$ of a motif $\pmotif$, if we want to match the suffix of $\pmotif$ starting by $\factor{i}$, $\factor{i}\factor{i-1}\cdots\factor{1}$ and given that we know every match of $\factor{i-1}\cdots\factor{1}$, the optimal match is to choose the match of $\factor{i-1}\cdots\factor{1}$ that minimize (maximize) the maximal (minimal) element of the match of $\factor{i-1}\cdots\factor{1}$ and that allow a match of factor $\factor{i}$. In other word if we want to match $\pmotif[\first{i}:]$ with $\ptext[j:]$ such that $\first{i}$ is matched with element at index $j$ in $\ptext$, the optimal way of matching $\pmotif[\first{i-1}:]$ is to choose the minimal (maximal) element at index $j'$ of $\ptext[j:]$ such that : (1) $\pmotif[\first{i-1}:]$ is matched with $\ptext[j':]$ and element $\first{i-1}$ is matched with element at index $j'$, (2) the factor $\factor{i}$ is matched with $\ptext[j,j'-1]$ and element $\first{i}$ is matched with element at index $j$, (3) Every elements of the match of (2) if inferior (superior) to the minimal (maximal) element of the match of (1). Indeed when we will match $\factor{i+1}\factor{i}\factor{i-1}\cdots\factor{1}$, every element of $\factor{i+1}$ must be matched to element superior (inferior) to every element matched element of $\factor{i}\factor{i-1}\cdots\factor{1}$, particularly its must be superior (inferior) to the maximal (minimal) element of the match of $\factor{i}\factor{i-1}\cdots\factor{1}$.

@@

There exists a match of $\pmotif$ in $\ptext$ if and only if
there exists a $LM(n,i)\neq 0$ for $1 \leq i \leq |\ptext|$,
with $n$ the number of factor in $\pmotif$.
Moreover the basic case can be computed in $O(|\ptext|^2)$
and the induction on $O(|\pmotif||\ptext|^2)$.
\end{proof}

@@

\section{Pattern Matching With Bivincular Motif Avoiding (231,213)}	
\label{section:bivincular}

This section gives an algorithm to detect bivincular permutation in polynomial time in the case where the motif avoid $(213,231)$.
We denote $\pbmotif=\bmotif$ the bivincular motif.

\begin{proposition}
Let $\pbmotif$ be a bivincular motif such that $\pmotif$
avoid (231,213), 
$\ptext$ a permutation,
we can decide in $O(|\pmotif||\ptext|^3)$ time
and $O(|\ptext|^3)$ space
if $\pbmotif$
appear in $\ptext$.
\end{proposition}

			\begin{proof}
			We consider the following problem :\\

			Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\

			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= \left\{ 
				\begin{array}{l l}
					true & \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
						& \text{with every element in}\\ 
						&[\min,\max]\\

@@

			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}$ is closed under induction. 
			it can be
			solved by means of the following relations:\\

@@

			if $n_\pmotif \notin  \x $
			and $n_\pmotif \notin  \y$ : \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\

			if $n_\pmotif \in  \x $
			and $n_\pmotif \notin  \y$ : \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,n_\ptext)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[n_\ptext]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\

			if $n_\pmotif \notin  \x$  
			and $n_\pmotif \in  \y$ 
			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						and }\\
						&\text{$\ptext[j]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\

			if $n_\pmotif \in  \x$  
			and $n_\pmotif \in  \y$ 
			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,n_\ptext)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[n_\ptext]<\max$
						and }\\
						&\text{$\ptext[n_\ptext]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\

			\textbf{STEP :} \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= \\ \left\{ 
					\begin{array}{l l}

						\bigcup_{j<k}\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$
							and $i \notin \x$}\\
							& \text{and $i \notin \y$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\bigcup_{j<k}\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \notin \x$ and $i \notin \y$  }\\
							& \text{and $\min<\ptext[j]<\max$} \\		
						&\\

						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
							& \text{and $i \in \x$ and $i \notin \y$}\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \in \x$ and $i \notin \y$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\

@@

						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,\ptext^{-1}[\ptext[j]+1]) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \notin \x$ and $i \in \y$}\\
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}[\ptext[j]+1]>j$}\\
						&\\

						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,\ptext^{-1}[\ptext[j]-1]) 
							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \notin \x$ and $i \in \y$ }\\	
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}[\ptext[j]-1]>j$}\\
						&\\

						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,j+1) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]+1=\ptext[j+1]$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,j+1)
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\	
						False & Otherwise\\																		
					\end{array} \right. $\\

@@

			\end{proof}

@@

	$\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}$
	= max$\{$ $|s|$ $|$ 
	s is a pattern occurring 
	in  $\pi_1[i_1:]$
	by the subsequence $s_1$ and $\min(s_1)=\min_1$ and $\max(s_1)=\max_1$
	and s is occurring
	in  $\pi_2[i_2:]$
	by the subsequence $s_2$ and $\min(s_2)=\min_2$ and $\max(s_2)=\max_2$	
	$\}$\\

@@

	\textbf{BASE :} \\
	$	\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{|\pi_1|}{|\pi_2|} = \left\{ 
			\begin{array}{l l}
				1 & \text{if $\min_1=\pi_1[j]=\max_1$  
				}\\
				& \text{ and $\min_2=\pi_2[j]=\max_2$}\\
				0 & otherwise\\
			\end{array} \right. $\\

@@

	$\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}
	=$
	$ \max \left\{ 
			\begin{array}{l l}
				\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2+1} \\
				\\
				\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1+1}{i_2} \\
				\\
				\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}
			\end{array} \right. $\vspace{20pt}\\

	with
	$\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}=\\ \left\{ 
				\begin{array}{l l}
					1+\LCS{\pi_1}{\pi_1[i_1]}{\max_1}{\pi_2}{\pi_2[i_2]}{\max_2}{i_1}{i_2+1} & \text{$\pi_1[i_1]<\min_1$ } \\
					& \text{and $\pi_2[i_2]<\min_2$} \\
					&\\
					1+\LCS{\pi_1}{\min_1}{\pi_1[i_1]}{\pi_2}{\min_2}{\pi_2[i_2]}{i_1+1}{i_2}
					 & \text{$\pi_1[i_1]>\max_1$ } \\	
					&\text{and $\pi_2[i_2]>\max_2$}\\	
					&\\	
					0 & \text{otherwise}\\							
				\end{array} \right.$\\

>>>>

\newcommand{\x}{X}
\newcommand{\y}{Y}
\newcommand{\bmotif}{(\sigma,\x,\y)}

@@

@@

A \emph{bivincular pattern} (abbreviated BVP) $\sigma$
of length $k$ is a permutation in $S_k$ written in
two-line notation 
(that is the top row is $12\,\ldots\,k$ and the bottom row
is a permutation $\sigma_1\sigma_2\,\ldots\,\sigma_k$).
We have the following conditions on the top and bottom rows
of $\sigma$:
\begin{itemize}
	\item
	If the bottom line of $\sigma$ contains
	$\underline{\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j}$
	then the letters corresponding to 
	$\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j$ in an occurrence of
	$\sigma$ in a permutaton must be adjacent, whereas there is
	no adjacency condition for
	non-underlined consecutive letters.
	Moreover if the bottom row of $\sigma$ begins with
	$_\llcorner{\sigma_1}$ then any occurrence of $\sigma$ 
	in a permutation $\pi$ must begin with the leftmost 
	letter of $\pi$,
	and 
	if the bottom row of $\sigma$ begins with
	${\sigma_k}_\lrcorner$ then any occurrence of $\sigma$ 
	in a permutation $\pi$ must end with the rightmost 
	letter of $\pi$.
	\item
	If the top line of $\sigma$ contains
	$\overline{i\,i+1\,\ldots\,j}$ then the letters corresponding to
	$\sigma_i, \sigma_{i+1}, \ldots, \sigma_j$ in an
	occurrence of $\sigma$ in a permutation must be adjacent in values,
	whereas there is no value adjacency restriction for non-overlined 
	letters.
	Moreover, if the top row of $\sigma$ begins with
	$^\ulcorner{1}$ then
	any occurrence of $\sigma$ is a permutation $\pi$ must begin with
	the smallest letter of $\pi$, and
	if top row of $\sigma$ ends with $k^\urcorner$ then
	any occurrence of $\sigma$ is a permutation $\pi$ must end with
	the largest letter of $\pi$.
\end{itemize}
% A bivincular pattern avoids a set of permutations $P$ if its bottom
% row $\sigma_1\sigma_2\,\ldots\,\sigma$ avoids every permutation in $P$.

@@

This section focus on the pattern containment problem 
in case only the pattern $\sigma$ avoids $231$ and $213$.

\begin{proposition}
	\label{Proposition:sigma avoids 213 and 231}
	Let $\sigma \in \AV_k(213,231)$ and $\pi \in S_n$.
	One can decide in $O(kn^2)$ time
	and $O(kn^2)$ space if $\pi$ contains $\sigma$.
\end{proposition}

For the proof and the algorithm we introduce a decomposition : we decompose the stripe of the motif into factor of same letter, and label those factor from right to left. We also need to add the last index into the first factor. For each factor, we denote the left most element by $\firsta$. For example, given the motif $981237654$, $\factor{1} =7654$, $\first{1}=7$, $\factor{2}=123$, $\first{2}=1$, $\factor{3}=98$ and $\first{9}$.

\begin{proof}[of Proposition~\ref{Proposition:sigma avoids 213 and 231}]
Given an ascent (descent) factor $\factor{i}$ of a motif $\pmotif$, if we want to match the suffix of $\pmotif$ starting by $\factor{i}$, $\factor{i}\factor{i-1}\cdots\factor{1}$ and given that we know every match of $\factor{i-1}\cdots\factor{1}$, the optimal match is to choose the match of $\factor{i-1}\cdots\factor{1}$ that minimize (maximize) the maximal (minimal) element of the match of $\factor{i-1}\cdots\factor{1}$ and that allow a match of factor $\factor{i}$. In other word if we want to match $\pmotif[\first{i}:]$ with $\ptext[j:]$ such that $\first{i}$ is matched with element at index $j$ in $\ptext$, the optimal way of matching $\pmotif[\first{i-1}:]$ is to choose the minimal (maximal) element at index $j'$ of $\ptext[j:]$ such that : (1) $\pmotif[\first{i-1}:]$ is matched with $\ptext[j':]$ and element $\first{i-1}$ is matched with element at index $j'$, (2) the factor $\factor{i}$ is matched with $\ptext[j,j'-1]$ and element $\first{i}$ is matched with element at index $j$, (3) Every elements of the match of (2) if inferior (superior) to the minimal (maximal) element of the match of (1). Indeed when we will match $\factor{i+1}\factor{i}\factor{i-1}\cdots\factor{1}$, every element of $\factor{i+1}$ must be matched to element superior (inferior) to every element matched element of $\factor{i}\factor{i-1}\cdots\factor{1}$, particularly its must be superior (inferior) to the maximal (minimal) element of the match of $\factor{i}\factor{i-1}\cdots\factor{1}$.

@@

There exists a match of $\pmotif$ in $\ptext$ if and only if
there exists a $LM(n,i)\neq 0$ for $1 \leq i \leq |\ptext|$,
with $n$ the number of factor in $\pmotif$.
Moreover the basic case can be computed in $O(|\ptext|^2)$
and the induction on $O(|\pmotif||\ptext|^2)$.
\qed
\end{proof}

@@

\section{$(213,231)$-avoiding bivincular patterns}	
	\label{section:bivincular}

	This section is devoted to presenting a polynomial-time algorithm for deciding whether
	a $(213,231)$-avoiding bivincular pattern occurs in a permutation.

	\begin{proposition}
		\label{Proposition:bivincular pattern}
			Let $\sigma$ be a $(213,231)$-avoiding bivincular pattern of length $k$
			and $\pi \in S_n$.
			One can decide in $O(kn^3)$ time
			and $O(kn^3)$ space if $\pi$ contains $\sigma$.
	\end{proposition}

			\begin{proof}
			We consider the following problem :
			Given a bivincular motif $\bmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\

			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(i,j)= \left\{ 
				\begin{array}{l l}
					true & \text{If $\pmotif[i:]$ is a motif of $\ptext[j:]$}\\
						& \text{with every element in}\\ 
						&[\min,\max]\\

@@

			$\mathbb{P}_{\pmotif,\ptext,\min,\max}$ is closed under induction. 
			it can be
			solved by means of the following relations:\\

@@

			if $n_\pmotif \notin  \x $
			and $n_\pmotif \notin  \y$ : \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,j)= true $\\

			if $n_\pmotif \in  \x $
			and $n_\pmotif \notin  \y$ : \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,n_\ptext)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[n_\ptext]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,n_\ptext)= true $\\

			if $n_\pmotif \notin  \x$  
			and $n_\pmotif \in  \y$ 
			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						and }\\
						&\text{$\ptext[j]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,j)= true $\\

			if $n_\pmotif \in  \x$  
			and $n_\pmotif \in  \y$ 
			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,n_\ptext)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[n_\ptext]<\max$
						and }\\
						&\text{$\ptext[n_\ptext]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,n_\ptext)= true $\\

			\textbf{STEP :} \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(i,j)= \\ \left\{ 
					\begin{array}{l l}

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$
							and $i \notin \x$}\\
							& \text{and $i \notin \y$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \notin \x$ and $i \notin \y$  }\\
							& \text{and $\min<\ptext[j]<\max$} \\		
						&\\

						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
							& \text{and $i \in \x$ and $i \notin \y$}\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \in \x$ and $i \notin \y$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\

@@

						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,\ptext^{-1}[\ptext[j]+1]) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \notin \x$ and $i \in \y$}\\
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}[\ptext[j]+1]>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,\ptext^{-1}[\ptext[j]-1]) 
							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \notin \x$ and $i \in \y$ }\\	
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}[\ptext[j]-1]>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,j+1) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]+1=\ptext[j+1]$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,j+1)
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\	
						False & Otherwise\\																		
					\end{array} \right. $\\

@@

@@

	$S_{\pi_1,\pi_2}(\min_1,\max_1,\min_2,\min_2,i_1,i_2)$
	= max$\{$ $|s|$ $|$ 
	s is a pattern occurring 
	in  $\pi_1[i_1:]$
	by the subsequence $s_1$ and $\min(s_1)=\min_1$ and $\max(s_1)=\max_1$
	and s is occurring
	in  $\pi_2[i_2:]$
	by the subsequence $s_2$ and $\min(s_2)=\min_2$ and $\max(s_2)=\max_2$	
	$\}$\\

@@

	\textbf{BASE :} \\
	$S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(|\pi_1|,|\pi_2|) = \left\{ 
			\begin{array}{l l}
				1 & \text{if $\min_1=\pi_1[j]=\max_1$  
				}\\
				& \text{ and $\min_2=\pi_2[j]=\max_2$}\\
				0 & otherwise\\
			\end{array} \right. $\\

@@

	$S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2) =$\\
	\indent $ \max \left\{ 
			\begin{array}{l l}
				S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2+1) \\
				S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_22}(i_1+1,i_2) \\
				S'_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2)
			\end{array} \right. $\vspace{20pt}\\

	with 
	$S'_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2)=\\ \left\{ 
				\begin{array}{l l}
					1+S_{\pi_1,\pi_2,\pi_1[i_1],\max_1,\pi_2[i_2]}(i_1+1,i_2+1)  & \text{$\pi_1[i_1]<\min_1$ } \\
					& \text{and $\pi_2[i_2]<\min_2$} \\
					&\\
					1+S_{\pi_1,\pi_2,\min_1,\pi_1[i_1],\min_2,\pi_2[i_2]}(i_1+1,i_2+1)  & \text{$\pi_1[i_1]>\max_1$ } \\	
					&\text{and $\pi_2[i_2]>\max_2$}\\	
					&\\	
					0 & \text{otherwise}\\							
				\end{array} \right.$\\
